%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Kynetics} % Organization
    {Padua, Italy} % Location
    {Feb. 2017 - Aug 2023} % Date(s)
    {
    \begin{cvitems}
    		\item Web application development in Scala/Kotlin (Play and SpringBoot).
    		\item DevOps activities on AWS cloud. AWS cloud configuration using Sceptre, Pulumi, Gradle and Python. Application release automation on EKS (Pulumi, Helm, Docker, Gradle). Reduced client application deployment time from days to minutes.
    		\item Android application development in Kotlin/Java.
    		\item Mantainer \href{https://github.com/eclipse-hara/hara-ddiclient}{\underline{hara-ddiclient}} (Eclipse Foundation project).
    \end{cvitems}
    }
\hfill \break
%---------------------------------------------------------
  \cventry
    {Mobile / Web Developer} % Job title
    {IDX Italy} % Organization
	{Padua, Italy} % Location
    {Sep. 2015 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Restful API (JSON) development with Java (SpringBoot)}.
        \item {E-commerce development (order collection) in Angular}.
        \item {Android application development (SQLite, Retrofit)}.
        \item {Study and implementation of demos in the field of IoT and augmented reality}.
      \end{cvitems}
    }
\hfill \break
%---------------------------------------------------------
  \cventry
    {Android / Java Developer} % Job title
    {IKS srl} % Organization
	{Padua, Italy} % Location
    {Feb. 2014 - Sep. 2015} % Date(s)	
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web application development and API (restful/JSON) for communication with mobile devices (spring and JSF)}.
        \item {Android application development and maintenance (SQLite, Retrofit)}.
        \item {Development API (restful/JSON) in PHP with Symfony}.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
